<<<<<<< HEAD
--- title: "zty  code" author: "Taiyuan Zhang" date: '2023-07-13' output:
html_document ---

# Line33  91 157 165
data
首先检查数据类型
```{r} 
# Define the center of the sphere center <- c(data[i, "x"], data[i, "y"],data[i, "z"])
# Print the center vector to check its value print(center)
# Check the data$x, data$y, data$z vectors for non-numeric values
library(data.table)
data <- as.data.table(`6vxx`)
#data就是6vxx的A chain, 972个
print(any(!is.numeric(data$x))) 
print(any(!is.numeric(data$y)))
print(any(!is.numeric(data$z)))
nrow(data)
# Convert the x column to numeric, replacing non-numeric values with NA
x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
# Check the data types of the x, y, and z columns
class(data$x)
class(data$y)
class(data$z)
#class(center)
```

计算origin情况球内点的数量和点的virusNumber和
原有问题1：center是list类，要转化为numerical类
改进0720：寻找最佳参数
在radius等于5时，平均球内数为3.504115
```{r}
# Define a vector of radii
radii <- c(5, 6,7,8,9,10)

# Initialize an empty list to store the sums1 vectors for each radius
sums1_list <- list()
num_in_sphere_list<-list()

# Loop through each radius and calculate the sum of num values for the points within the sphere
for (r in radii) {
  # Initialize an empty vector to store the sum of num values for each sphere
  sums1 <- c()
  
  # Initialize an empty vector to store the number of points within each sphere
  num_in_sphere <- numeric(nrow(data))
  
  # Loop through each point and calculate the sum of num values for the points within the sphere
  for (i in 1:nrow(data)) {
    # Define the center of the sphere
    center <- c(data[i, "x"], data[i, "y"], data[i, "z"])
    
    # Define the center of the sphere as a numeric vector
    center <- unlist(data[i, c("x", "y", "z")])
    
    # Convert the x, y, and z variables to numeric
    x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
    y <- ifelse(is.na(as.numeric(data$y)), NA, as.numeric(data$y))
    z <- ifelse(is.na(as.numeric(data$z)), NA, as.numeric(data$z))
    
    # Calculate the Euclidean distance between each point and the center
    distances <- sqrt((x - center[1])^2 + (y - center[2])^2 + (z - center[3])^2)
    
    # Subset the data to only include points within the sphere
    subset_data <- data[distances <= r, ]
    
    # Calculate the sum of num values for the points within the sphere
    sum_num <- sum(subset_data$num)
    # Add the number of points within the sphere to the vector of counts
    num_in_sphere[i] <- nrow(subset_data)
    # Add the sum to the vector of sums
    sums1 <- c(sums1, sum_num)
  }
  
  # Add the sums1 vector to the list for the current radius
  sums1_list[[as.character(r)]] <- sums1
  
  # Print the vector of num_in_sphere for the current radius
  #cat("Number of points within sphere (radius =", r, "):", num_in_sphere, "\n")
  # Print the mean of num_in_sphere for the current radius
  cat("Mean number of points within sphere (radius =", r, "):", mean(num_in_sphere), "\n\n")
}
num_in_sphere_list[[as.character(r)]] <- num_in_sphere
# Print the sums1 vectors for each radius in the list
# for (r in radii) {
#   cat("Radius", r, ": ", sums1_list[[as.character(r)]], "\n")
# }
```

尝试重复20次sums2。
```{r}
## Initialize an empty vector to store the sum of changesum vectors for 20 iterations
changesum_sumlist <- list()

# Initialize an empty list to store the num_in_sphere vectors for each radius
num_in_sphere_list <- list()
change_num_list <- list()

# Define a vector of radii
radii <- c(5, 6, 7, 8, 9, 10)

# Loop through each radius
for (r in radii) {
  # Initialize an empty list to store the sums2 vectors for each iteration
  sums2_list <- list()
  
  # Initialize an empty vector to store the changesum values for 20 iterations
  changesum_vec <- numeric(length = 20)
  
  # Initialize an empty vector to store the num_in_sphere values for each iteration
  num_in_sphere_vec <- numeric(length = nrow(data))
  
  # Loop 20 times to calculate changesum for each iteration
  for (i in 1:20) { 
    # Initialize an empty vector to store the sums2 values for each point
    sums2 <- numeric(length = nrow(data))
    
    # Loop through each point and calculate the sum of ran_num values for the points within the sphere
    for (j in 1:nrow(data)) {
      # Define the center of the sphere
      center <- unlist(data[j, c("x", "y", "z")])
      
      # Convert the x, y, and z variables to numeric
      x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
      y <- ifelse(is.na(as.numeric(data$y)), NA, as.numeric(data$y))
      z <- ifelse(is.na(as.numeric(data$z)), NA, as.numeric(data$z))
      
      # Calculate the Euclidean distance between each point and the center
      distances <- sqrt((x - center[1])^2 + (y - center[2])^2 + (z - center[3])^2)
      
      # Subset the data to only include points within the sphere
      subset_data <- data[distances <= r, ]
      
      # Calculate the sum of ran_num values for the points within the sphere
      sum_num <- sum(subset_data$ran_num)
      
      # Add the sum to the vector of sums2
      sums2[j] <- sum_num
      
      # Count the number of points within the sphere
      num_in_sphere_vec[j] <- nrow(subset_data)
    }
    
    # Add the sums2 vector to the list for the current iteration
    sums2_list[[as.character(i)]] <- sums2
    
    # Calculate the changesum vector for this iteration
    changesum <- sums2 - sums1_list[[as.character(r)]]
    
    # Add the changesum vector to the changesum sum vector
    changesum_sumlist[[as.character(r)]] <- if (i == 1) changesum else changesum_sumlist[[as.character(r)]] + changesum
    
    # Add the sum of changesum vector to the changesum vector
    changesum_vec[i] <- sum(changesum)
  }
  
  # Store the num_in_sphere vector for this radius
  num_in_sphere_list[[as.character(r)]] <- num_in_sphere_vec
  
  # Calculate the mean of the changesum vectors for this radius
  mean_changesum <- mean(changesum_vec)
  
  # Calculate the mean of the num_in_sphere vector for this radius
  mean_num_in_sphere <- mean(num_in_sphere_list[[as.character(r)]], na.rm = TRUE)
  
  # Calculate the change percentage for this radius for each point
  change_num <- changesum_sumlist[[as.character(r)]] / (num_in_sphere_list[[as.character(r)]] * 20)
  change_num_list[[as.character(r)]] <- change_num
  # Print the mean change percentage for this radius
  cat("Radius", r, ": Mean change num = ", mean(change_num, na.rm = TRUE), "\n")
  
  # Print the change_num vector for each point
  #print(change_num)
   # Find the top 5% value of the change_num vector
  top_5_percent <- quantile(change_num, probs = 0.05, type = 1)
  
  # Find the indices of the values in the change_num vector that are less than the top 5% value
  top_5_percent_indices <- which(change_num < top_5_percent)
  
  # Print the indices

  cat("Radius", r, ": Top 5% indices = ", top_5_percent_indices, "\n")
# # Loop through each top 5% index and extract the corresponding row from data
#   for (index in top_5_percent_indices) {
#     data_filtered <- data[c(index), ]
#     
#     # Print the filtered data
#     cat("Radius", r, ": Filtered data for index", index, ":\n")
#     #print(data_filtered)
#  }
}
#problem:too much for one loop
```
  # Extract the corresponding rows from data and store在循环完成后，我们遍历每个radius并提取相应的筛选结果。我们可以使用一个for循环来遍历每个radius，然后从`top_5_percent_indices`中提取对应的行，并将它们存储在`data_filtered_list`中的相应位置。以下是修改后的代码：

```{r}
data_filtered_list <- list()
# Loop through each radius and extract the corresponding rows from data
for (r in radii) {
  # Extract the indices of the filtered rows for this radius
  top_5_percent_indices <- which(change_num_list[[as.character(r)]] < quantile(change_num_list[[as.character(r)]], probs = 0.05, type = 1))
  
  # Extract the filtered data for this radius and store in data_filtered
  data_filtered <- data[top_5_percent_indices, ]
  
  # Store data_filtered in the data_filtered_list
  data_filtered_list[[as.character(r)]] <- data_filtered
}

# Print data_filtered_list
print(data_filtered_list)
```
发现序号上(1D),也存在一定的集聚性
并且不同的radius找出的序号有相似性
```{r}
#2.cluster for actual points
library(plot3D)
library(dbscan)

# Define a vector of radii
radii <- c(5, 6, 7, 8, 9, 10)

# Loop through each radius
for (r in radii) {
  # Extract the filtered data for this radius
  data_filtered <- data_filtered_list[[as.character(r)]]
  
  # Perform DBSCAN clustering on the data
  dbscan_result <- dbscan(data.frame(data_filtered$x, data_filtered$y, data_filtered$z), eps = 7, minPts = 5)
  
  # Create a 3D scatter plot of the data with cluster assignments
  scatter3D(data_filtered$x, data_filtered$y, data_filtered$z, col = dbscan_result$cluster)
  
  # Add a title to the plot
  title(main = paste("DBSCAN clustering for radius =", r))
}
```
#0区cluster都是noise point
```{r}
# #打印出相关点的3D坐标
library(dbscan)

# Define a vector of radii
radii <- c(5, 6, 7, 8, 9, 10)

# Loop through each radius
for (r in radii) {
  # Extract the filtered data for this radius
  data_filtered <- data_filtered_list[[as.character(r)]]
  
  # Perform DBSCAN clustering on the data
  dbscan_result <- dbscan(data.frame(data_filtered$x, data_filtered$y, data_filtered$z), eps = 7, minPts = 5)
  
  # Get the cluster assignments for each point
  clusters <- dbscan_result$cluster
  
  # Create a list of groups
  groups <- split(data_filtered, f = clusters)
  
  # Remove empty groups
  groups <- groups[sapply(groups, nrow) > 0]
  
  # Print the groups for this radius
  cat("Radius", r, ":\n")
  for (i in seq_along(groups)) {
    cat("Cluster", i, ":\n")
    print(groups[[i]])
    cat("\n")
  }
}
```
#结果：group1 散点，无法成团
#group2-9:成团点


719：
To do:
1. better present result
2.repeat to find radius
 