---
title: "Hot-Spot-ball"
author: "Liangxiao LI"
date: "2023-07-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

change parameter at 81,334, see check mean radius？
see row 78 to merge!
```{r}
library(data.table)
library(sp)
library(spgwr)
#library(spdep)
library(readxl)
#library(spatialreg)
library(gstat)
library(stats)
library(dbscan)
library(cluster)
library(ggplot2)
library(scatterplot3d)
library(rgl)
library(mclust)
library(plotly)
library(dplyr)
library(FNN)
library(matrixStats)
library(tidyr)
library(scales)
library(factoextra)
library(spatstat)
library(clValid)
library(factoextra)
library(fpc)
library(NbClust)
library(readxl)
library(plot3D)
library(DT)
```

#First check data type
```{r} 
# Define the center of the sphere center <- c(data[i, "x"], data[i, "y"],data[i, "z"])
# Print the center vector to check its value print(center)
# Check the data$x, data$y, data$z vectors for non-numeric values
#library(data.table)
#data <- as.data.table(`6vxx`)
#Xiao
setwd("/Users/ryan/Documents/GitHub/Shenzhen Bay lab/spike_protein_3structures_markerd_with_variants_from_cncb")
data <- read_excel("6vxx_variants.xls") 
data <- data[1:972,c("X","Y","Z","virusNumber")]
colnames(data)[1] <- "x"
colnames(data)[2] <- "y"
colnames(data)[3] <- "z"
colnames(data)[4] <- "num"
#data就是6vxx的A chain, 972个
print(any(!is.numeric(data$x))) 
print(any(!is.numeric(data$y)))
print(any(!is.numeric(data$z)))
nrow(data)
# Convert the x column to numeric, replacing non-numeric values with NA
x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
# Check the data types of the x, y, and z columns
class(data$x)
class(data$y)
class(data$z)
#class(center)
```




#Multiple R- (Not merged yet)


计算origin情况球内点的数量和点的virusNumber和
原有问题1：center是list类，要转化为numerical类
改进0720：寻找最佳参数
在radius等于5时，平均球内数为3.504115
```{r}
# Define a vector of radii
radii <- c(5, 6,7,8,9,10)

# Initialize an empty list to store the sums1 vectors for each radius
sums1_list <- list()
num_in_sphere_list<-list()

# Loop through each radius and calculate the sum of num values for the points within the sphere
for (r in radii) {
  # Initialize an empty vector to store the sum of num values for each sphere
  sums1 <- c()
  
  # Initialize an empty vector to store the number of points within each sphere
  num_in_sphere <- numeric(nrow(data))
  
  # Loop through each point and calculate the sum of num values for the points within the sphere
  for (i in 1:nrow(data)) {
    # Define the center of the sphere
    center <- c(data[i, "x"], data[i, "y"], data[i, "z"])
    
    # Define the center of the sphere as a numeric vector
    center <- unlist(data[i, c("x", "y", "z")])
    
    # Convert the x, y, and z variables to numeric
    x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
    y <- ifelse(is.na(as.numeric(data$y)), NA, as.numeric(data$y))
    z <- ifelse(is.na(as.numeric(data$z)), NA, as.numeric(data$z))
    
    # Calculate the Euclidean distance between each point and the center
    distances <- sqrt((x - center[1])^2 + (y - center[2])^2 + (z - center[3])^2)
    
    # Subset the data to only include points within the sphere
    subset_data <- data[distances <= r, ]
    
    # Calculate the sum of num values for the points within the sphere
    sum_num <- sum(subset_data$num)
    # Add the number of points within the sphere to the vector of counts
    num_in_sphere[i] <- nrow(subset_data)
    # Add the sum to the vector of sums
    sums1 <- c(sums1, sum_num)
  }
  
  # Add the sums1 vector to the list for the current radius
  sums1_list[[as.character(r)]] <- sums1
  
  # Print the vector of num_in_sphere for the current radius
  #cat("Number of points within sphere (radius =", r, "):", num_in_sphere, "\n")
  # Print the mean of num_in_sphere for the current radius
  cat("Mean number of points within sphere (radius =", r, "):", mean(num_in_sphere), "\n\n")
}
num_in_sphere_list[[as.character(r)]] <- num_in_sphere
# Print the sums1 vectors for each radius in the list
# for (r in radii) {
#   cat("Radius", r, ": ", sums1_list[[as.character(r)]], "\n")
# }
```

尝试重复20次sums2。
```{r}
## Initialize an empty vector to store the sum of changesum vectors for 20 iterations
changesum_sumlist <- list()

# Initialize an empty list to store the num_in_sphere vectors for each radius
num_in_sphere_list <- list()
change_num_list <- list()

# Define a vector of radii
radii <- c(5, 6, 7, 8, 9, 10)

# Loop through each radius
for (r in radii) {
  # Initialize an empty list to store the sums2 vectors for each iteration
  sums2_list <- list()
  
  # Initialize an empty vector to store the changesum values for 20 iterations
  changesum_vec <- numeric(length = 20)
  
  # Initialize an empty vector to store the num_in_sphere values for each iteration
  num_in_sphere_vec <- numeric(length = nrow(data))
  
  # Loop 20 times to calculate changesum for each iteration
  for (i in 1:20) { 
    # Initialize an empty vector to store the sums2 values for each point
    sums2 <- numeric(length = nrow(data))
    
    # Loop through each point and calculate the sum of ran_num values for the points within the sphere
    for (j in 1:nrow(data)) {
      # Define the center of the sphere
      center <- unlist(data[j, c("x", "y", "z")])
      
      # Convert the x, y, and z variables to numeric
      x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
      y <- ifelse(is.na(as.numeric(data$y)), NA, as.numeric(data$y))
      z <- ifelse(is.na(as.numeric(data$z)), NA, as.numeric(data$z))
      
      # Calculate the Euclidean distance between each point and the center
      distances <- sqrt((x - center[1])^2 + (y - center[2])^2 + (z - center[3])^2)
      
      # Subset the data to only include points within the sphere
      subset_data <- data[distances <= r, ]
      
      # Calculate the sum of ran_num values for the points within the sphere
      sum_num <- sum(subset_data$ran_num)
      
      # Add the sum to the vector of sums2
      sums2[j] <- sum_num
      
      # Count the number of points within the sphere
      num_in_sphere_vec[j] <- nrow(subset_data)
    }
    
    # Add the sums2 vector to the list for the current iteration
    sums2_list[[as.character(i)]] <- sums2
    
    # Calculate the changesum vector for this iteration
    changesum <- sums2 - sums1_list[[as.character(r)]]
    
    # Add the changesum vector to the changesum sum vector
    changesum_sumlist[[as.character(r)]] <- if (i == 1) changesum else changesum_sumlist[[as.character(r)]] + changesum
    
    # Add the sum of changesum vector to the changesum vector
    changesum_vec[i] <- sum(changesum)
  }
  
  # Store the num_in_sphere vector for this radius
  num_in_sphere_list[[as.character(r)]] <- num_in_sphere_vec
  
  # Calculate the mean of the changesum vectors for this radius
  mean_changesum <- mean(changesum_vec)
  
  # Calculate the mean of the num_in_sphere vector for this radius
  mean_num_in_sphere <- mean(num_in_sphere_list[[as.character(r)]], na.rm = TRUE)
  
  # Calculate the change percentage for this radius for each point
  change_num <- changesum_sumlist[[as.character(r)]] / (num_in_sphere_list[[as.character(r)]] * 20)
  change_num_list[[as.character(r)]] <- change_num
  # Print the mean change percentage for this radius
  cat("Radius", r, ": Mean change num = ", mean(change_num, na.rm = TRUE), "\n")
  
  # Print the change_num vector for each point
  #print(change_num)
   # Find the top 5% value of the change_num vector
  top_5_percent <- quantile(change_num, probs = 0.05, type = 1)
  
  # Find the indices of the values in the change_num vector that are less than the top 5% value
  top_5_percent_indices <- which(change_num < top_5_percent)
  
  # Print the indices

  cat("Radius", r, ": Top 5% indices = ", top_5_percent_indices, "\n")
# # Loop through each top 5% index and extract the corresponding row from data
#   for (index in top_5_percent_indices) {
#     data_filtered <- data[c(index), ]
#     
#     # Print the filtered data
#     cat("Radius", r, ": Filtered data for index", index, ":\n")
#     #print(data_filtered)
#  }
}
#problem:too much for one loop
```
  # Extract the corresponding rows from data and store在循环完成后，我们遍历每个radius并提取相应的筛选结果。我们可以使用一个for循环来遍历每个radius，然后从`top_5_percent_indices`中提取对应的行，并将它们存储在`data_filtered_list`中的相应位置。以下是修改后的代码：

```{r}
data_filtered_list <- list()
# Loop through each radius and extract the corresponding rows from data
for (r in radii) {
  # Extract the indices of the filtered rows for this radius
  top_5_percent_indices <- which(change_num_list[[as.character(r)]] < quantile(change_num_list[[as.character(r)]], probs = 0.05, type = 1))
  
  # Extract the filtered data for this radius and store in data_filtered
  data_filtered <- data[top_5_percent_indices, ]
  
  # Store data_filtered in the data_filtered_list
  data_filtered_list[[as.character(r)]] <- data_filtered
}

# Print data_filtered_list
print(data_filtered_list)
```
发现序号上(1D),也存在一定的集聚性
并且不同的radius找出的序号有相似性
```{r}
#2.cluster for actual points
library(plot3D)
library(dbscan)

# Define a vector of radii
radii <- c(5, 6, 7, 8, 9, 10)

# Loop through each radius
for (r in radii) {
  # Extract the filtered data for this radius
  data_filtered <- data_filtered_list[[as.character(r)]]
  
  # Perform DBSCAN clustering on the data
  dbscan_result <- dbscan(data.frame(data_filtered$x, data_filtered$y, data_filtered$z), eps = 7, MinPts = 5)
  
  # Create a 3D scatter plot of the data with cluster assignments
  scatter3D(data_filtered$x, data_filtered$y, data_filtered$z, col = dbscan_result$cluster)
  
  # Add a title to the plot
  title(main = paste("DBSCAN clustering for radius =", r))
}
```
#0区cluster都是noise point
```{r}
# #打印出相关点的3D坐标
library(dbscan)

# Define a vector of radii
radii <- c(5, 6, 7, 8, 9, 10)

# Loop through each radius
for (r in radii) {
  # Extract the filtered data for this radius
  data_filtered <- data_filtered_list[[as.character(r)]]
  
  # Perform DBSCAN clustering on the data
  dbscan_result <- dbscan(data.frame(data_filtered$x, data_filtered$y, data_filtered$z), eps = 7, MinPts = 5)
  
  # Get the cluster assignments for each point
  clusters <- dbscan_result$cluster
  
  # Create a list of groups
  groups <- split(data_filtered, f = clusters)
  
  # Remove empty groups
  groups <- groups[sapply(groups, nrow) > 0]
  
  # Print the groups for this radius
  cat("Radius", r, ":\n")
  for (i in seq_along(groups)) {
    cat("Cluster", i, ":\n")
    print(groups[[i]])
    cat("\n")
  }
}
```
#结果：group1 散点，无法成团
#group2-9:成团点
























#Single r -Calculate center, each ball contain data point

```{r}
# Define the radius of the sphere 
#进行讨论
# Define the radius of the sphere
radius <- 10

# Initialize an empty vector to store the sum of num values for each sphere
sums1 <- c()

# Initialize an empty vector to store the number of points within each sphere
num_in_sphere <- numeric(nrow(data))

# Loop through each point and calculate the sum of num values for the points within the sphere
 # Convert the x, y, and z variables to numeric

for (i in 1:nrow(data)) {
  # Define the center of the sphere
  center <- c(data[i, "x"], data[i, "y"], data[i, "z"])
  
  # Define the center of the sphere as a numeric vector
  center <- unlist(data[i, c("x", "y", "z")])
  
  # Convert the x, y, and z variables to numeric
  x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
  y <- ifelse(is.na(as.numeric(data$y)), NA, as.numeric(data$y))
  z <- ifelse(is.na(as.numeric(data$z)), NA, as.numeric(data$z))
  
  # Calculate the Euclidean distance between each point and the center
  distances <- sqrt((x - center[1])^2 + (y - center[2])^2 + (z - center[3])^2)
  
  # Subset the data to only include points within the sphere
  subset_data <- data[distances <= radius, ]
  
  # Calculate the sum of num values for the points within the sphere
  sum_num <- sum(subset_data$num)
  # Add the number of points within the sphere to the vector of counts
  num_in_sphere[i] <- nrow(subset_data)
  # Add the sum to the vector of sums
  sums1 <- c(sums1, sum_num)
}

# Print the vector of sums1
print(sums1)
print(num_in_sphere)
```


```{r}
#随机排列放到第五列
# 新加一列
data<-as.data.table(data)

data[, sum1 := 1]
data[, ran_num := 1]
data[, sum2 := 1]
# 随机排序
rand_idx <- sample(nrow(data))

#将sums1写在第五列
data[,5]<-sums1

# 将随机排序的结果写入到第六列
data[, 6] <- data[rand_idx, 4]

#求sums2,随机排序的加和
radius <- 5

# Initialize an empty vector to store the sum of num values for each sphere
sums2 <- c()

# Loop through each point and calculate the sum of num values for the points within the sphere
 # Convert the x, y, and z variables to numeric

for (i in 1:nrow(data)) {
  # Define the center of the sphere
  center <- c(data[i, "x"], data[i, "y"], data[i, "z"])
  
  # Define the center of the sphere as a numeric vector
  center <- unlist(data[i, c("x", "y", "z")])
  
  # Convert the x, y, and z variables to numeric
  x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
  y <- ifelse(is.na(as.numeric(data$y)), NA, as.numeric(data$y))
  z <- ifelse(is.na(as.numeric(data$z)), NA, as.numeric(data$z))
  
  # Calculate the Euclidean distance between each point and the center
  distances <- sqrt((x - center[1])^2 + (y - center[2])^2 + (z - center[3])^2)
  
  # Subset the data to only include points within the sphere
  subset_data <- data[distances <= radius, ]
  
  # Calculate the sum of num values for the points within the sphere
  sum_num <- sum(subset_data$ran_num)
  # Add the sum to the vector of sums
  sums2 <- c(sums2, sum_num)
}

# Print the vector of sums1
print(sums2)

# 将随机排序的virusNumber和写入到第七列
data[, 7] <- sums2

# 保存新的数据
write.table(data, "new_data.txt", sep="\t", quote=FALSE, row.names=FALSE)
```

```{r}
# 绘制 sums1 的图形
plot(sums1)
# 计算 sums1 的长度并打印输出
length(sums1)
# 绘制 sums2 的图形
plot(sums2)
# 计算 sums2 的长度并打印输出
length(sums2)
# 打印数据框
print(data)
```

```{r}
# Initialize an empty vector to store the changesum values for 20 iterations
changesum_vec <- numeric(length=20)

# Initialize an empty vector to store the sum of changesum vectors for 20 iterations
changesum_sum <- numeric(length=nrow(data))

# Loop 20 times to calculate changesum for each iteration
for (i in 1:20) { 
  # Calculate changesum for each iteration
  
  # Initialize an empty vector to store the sum of num values for each sphere
  sums2 <- c()

  # Loop through each point and calculate the sum of num values for the points within the sphere
  radius <- 5
  for (j in 1:nrow(data)) {
    # Define the center of the sphere
    center <- unlist(data[j, c("x", "y", "z")])
    
    # Convert the x, y, and z variables to numeric
    x <- ifelse(is.na(as.numeric(data$x)), NA, as.numeric(data$x))
    y <- ifelse(is.na(as.numeric(data$y)), NA, as.numeric(data$y))
    z <- ifelse(is.na(as.numeric(data$z)), NA, as.numeric(data$z))
    
    # Calculate the Euclidean distance between each point and the center
    distances <- sqrt((x - center[1])^2 + (y - center[2])^2 + (z - center[3])^2)
    
    # Subset the data to only include points within the sphere
    subset_data <- data[distances <= radius, ]
    
    # Calculate the sum of num values for the points within the sphere
    sum_num <- sum(subset_data$ran_num)
    
    # Add the sum to the vector of sums
    sums2 <- c(sums2, sum_num)
  }
  
  # Calculate the changesum vector for this iteration
  changesum <- sums2 - sums1
  
  # Add the changesum vector to the changesum sum vector
  changesum_sum <- changesum_sum + changesum
  
  # Add the sum of changesum vector to the changesum vector
  changesum_vec[i] <- sum(changesum)
}

# Calculate the change percentage for each sphere
change_num <- changesum_sum / num_in_sphere

# Print the change percentage for each sphere
print(change_num)
```

```{r}
# 找出change_num向量的最小的5%值 
top_5_percent <- quantile(change_num,probs = 0.05, type = 1)
# 找出change_num向量中大于前5%值的元素的索引 
top_5_percent_indices <-which(change_num < top_5_percent)
# 输出结果 
print(top_5_percent_indices) 
```





























#DBscan high_mutation cluster

```{r}
#2.cluster for actual points
# # Subset the data to include only the points with the specified indices
# data_filter
# data_subset <- data_filter[, c("x", "y", "z")]
# 
# # Plot the points with different colors for each cluster assigned by DBSCAN
# plot(data_subset$x, data_subset$y, data_subset$z, col = dbscan_result$cluster)
# 
# # Perform k-means clustering on the data subset
# kmeans_result <- kmeans(data_subset, centers = 3)
# 
# # Print the cluster centers
# print(kmeans_result$centers)

# Load the required package
library(plot3D)

data_filtered <- data[c(top_5_percent_indices), ]

# Create a 3D scatter plot of the data with x, y, and z coordinates
scatter3D(data_filtered$x, data_filtered$y, data_filtered$z, col = "blue")

# Perform DBSCAN clustering on the data
dbscan_result <- dbscan(data_filtered[, c("x", "y", "z")], eps = 7,MinPts = 3)

dbscan_stats <- cluster.stats(dist(data_filtered[, c("x", "y", "z")]),  dbscan_result$cluster +1)

# Dunn index
dunn <- dbscan_stats$dunn
# Calinski-Harabasz index
ch <- dbscan_stats$ch
# Average silhouette width
sil <- dbscan_stats$avg.silwidth
#Entropy index
ent <- dbscan_stats$entropy



# Add the cluster assignments to the plot
points3D(data_filtered$x, data_filtered$y, data_filtered$z, col = dbscan_result$cluster)
#

```

#Model validation
```{r}

#Model validation - find best parameter
index <- data.frame()

epsilon <- 30

minpoint <- 10

topnum <- 50

#note that epsilon should be much bigger than minpoint, other wise if there's no ball with radius epsilon that contain minpoint, it will return warning no non-missing arguments to min; returning InfError: $ operator is invalid for atomic vectors

#also epsilon shouldn't be too big

for (i in 10:epsilon){
  
  for (j in 1:6){
    
    dbscan_result <- dbscan(data_filtered[, c("x", "y", "z")], eps = i,MinPts = j)
    
    #wss <- sum(dbscan_result$withinss)
    
    dbscan_stats <- cluster.stats(dist(data_filtered[, c("x", "y", "z")]),  dbscan_result$cluster +1)
    
    # Dunn index
    dunn <- dbscan_stats$dunn
    # Calinski-Harabasz index
    ch <- dbscan_stats$ch
    # Average silhouette width
    sil <- dbscan_stats$avg.silwidth
    #Entropy index
    ent <- dbscan_stats$entropy
    
    index <- rbind(index, c(i, j, dunn, ch, sil, ent))
    
  }
  
}

colnames(index) <- c("epsilon","minpoint","Dunn", "Calinski-Harabasz", "Average_Silhouette_Width", "Entropy")


```


```{r}

#par(mfrow = c(2, 2))

# Line chart for Dunn Index
plot(index$Dunn, type = "l", xlab = "Observation", ylab = "Dunn Index", main = "Dunn Index",xlim = c(0, length(index$Dunn) +1), ylim = c(min(index$Dunn)*0.95, max(index$Dunn)*1.2 ))

#创建表
top_dun <- data.frame()

# 标记最大值，并加进表里
sorted <- sort(index$Dunn, decreasing = TRUE)
top_three <- head(sorted, topnum)

print(top_three)

top_three <- unique(top_three)

for (i in 1:length(top_three)) {
  
  num <- which(index$Dunn == top_three[i])
  #text(x = num, y = top_three[i]*1.05, labels = paste0("T", i, ": ", round(top_three[i],5)), offset = 1)
  
  for (n in num){
    points(x = n, y= top_three[i], col = "red", pch = 19)
    
    top_dun <- rbind(top_dun, c(n,top_three[i]) )
    
  }
  
}
colnames(top_dun) <- c("Obs", "Dunn")
datatable(top_dun)

```


```{r}

# Line chart for Calinski-Harabasz Index
plot(index$`Calinski-Harabasz`, type = "l", xlab = "Observation", ylab = "Calinski-Harabasz Index", main = "Calinski-Harabasz Index",xlim = c(0, length(index$`Calinski-Harabasz`) +1), ylim = c(min(index$`Calinski-Harabasz`)*0.95, max(index$`Calinski-Harabasz`)*1.2 ))

#创建表
top_ch <- data.frame()

# 标记最大值
sorted <- sort(index$`Calinski-Harabasz`, decreasing = TRUE)
top_three <- head(sorted, topnum)

top_three <- unique(top_three)

for (i in 1:length(top_three)) {
  num <- which(index$`Calinski-Harabasz` == top_three[i])
  #text(x = num, y = top_three[i]*1.05, labels = paste0("T", i, ": ", round(top_three[i],5)), offset = 1)
  
  for (n in num){
    points(x = n, y= top_three[i], col = "red", pch = 19)
    
    top_ch <- rbind(top_ch, c(n,top_three[i]) )
  }
  
}

colnames(top_ch) <- c("Obs", "CH")
datatable(top_ch)

```


```{r}

# Line chart for Average Silhouette Width
plot(index$`Average_Silhouette_Width`, type = "l", xlab = "Observation", ylab = "Average Silhouette Width", main = "Average Silhouette Width",xlim = c(0, length(index$`Average_Silhouette_Width`) +1), ylim = c(min(index$`Average_Silhouette_Width`)*0.95, max(index$`Average_Silhouette_Width`)*1.2))

#创建表
top_ASW <- data.frame()

# 标记最大值
sorted <- sort(index$`Average_Silhouette_Width`, decreasing = TRUE)
top_three <- head(sorted, topnum)

top_three <- unique(top_three)

for (i in 1:length(top_three)) {
  num <- which(index$`Average_Silhouette_Width` == top_three[i])
  #text(x = num, y = top_three[i]*1.05, labels = paste0("T", i, ": ", round(top_three[i],5)), offset = 1)
  
  for (n in num){
    points(x = n, y= top_three[i], col = "red", pch = 19)
    
    top_ASW <- rbind(top_ASW, c(n,top_three[i]) )
  }
  
}

colnames(top_ASW) <- c("Obs", "ASW")
datatable(top_ASW)

```


```{r}

# Line chart for Entropy
plot(index$Entropy, type = "l", xlab = "Observation", ylab = "Entropy", main = "Entropy",xlim = c(0, length(index$Entropy) +1), ylim = c(min(index$Entropy)*0.95, max(index$Entropy)*1.2))

#创建表
min_E <- data.frame()

# 标记最大值
sorted <- sort(index$Entropy, decreasing = FALSE)
top_three <- head(sorted, topnum)

top_three <- unique(top_three)

for (i in 1:length(top_three)) {
  num <- which(index$Entropy == top_three[i])
  #text(x = num, y = top_three[i]*1.05, labels = paste0("T", i, ": ", round(top_three[i],5)), offset = 1)
  
  for (n in num){
    points(x = n, y= top_three[i], col = "red", pch = 19)
    
    min_E <- rbind(min_E, c(n,top_three[i]) )
  }
}


colnames(min_E) <- c("Obs", "Entropy")
datatable(min_E)

```

Dunn:the higher the better
(well-separated and compact)

CH:the higher the better
(well-separated and compact)

S:The higher the better
(well-separated and compact)

Entropy: the lower the better

Wss: the lower the better

weighted mean score = Dunn percentage + CH percentage + S percentage + entropy percentage

```{r}

D <- index$Dunn
A <- index$`Average_Silhouette_Width`
CH <- index$`Calinski-Harabasz`
E <- index$Entropy

#创建表
WS <- data.frame()

for (i in 1:length(D)){
  
  weight <- D[i]/max(D) + A[i]/max(A) + CH[i]/max(CH) + (1-E[i]/max(E))
  
  #WS <- rbind(WS, c(i + Kmin -1 ,weight) )
  WS <- rbind(WS, c(i,index$epsilon[i],index$minpoint[i],weight) )
  
}

colnames(WS) <- c("observation","epsilon","minpoint", "Weighted score")
datatable(WS)

# Line chart for WS
#plot(x=WS$`K-Num` ,y=WS$`Weighted score`, type = "l", xlab = "K-num", ylab = "Weighted score", main = "Weighted score",xlim = c(Kmin, Kmin+length(WS$`Weighted score`)-1), ylim = c(min(WS$`Weighted score`)*0.95, max(WS$`Weighted score`)*1.2))

plot(x=WS$`observation` ,y=WS$`Weighted score`, type = "l", xlab = "Observation", ylab = "Weighted score", main = "Weighted score",xlim = c(0, length(WS$`Weighted score`)+1), ylim = c(min(WS$`Weighted score`)*0.95, max(WS$`Weighted score`)*1.2))

Best_K <- data.frame()

# 标记最大值
sorted <- sort(WS$`Weighted score`, decreasing = TRUE)
top_three <- head(sorted,topnum)

top_three<- unique(top_three)

for (i in 1:length(WS$`Weighted score`)) {
  num <- which(WS$`Weighted score` == top_three[i])
  #text(x = num, y = top_three[i]*1.05, labels = paste0("T", i, ": ", round(top_three[i],5)), offset = 1)
  for (n in num){
    #points(x = n +Kmin -1, y= top_three[i], col = "red", pch = 19)
    points(x = n , y= top_three[i], col = "red", pch = 19)
    Best_K <- rbind(Best_K, c(i,index$epsilon[n],index$minpoint[n],n,top_three[i]) )
    
    
  }
}

colnames(Best_K) <- c("Best_descend", "epsilon","minpoint","Obs","Weighted score")
datatable(Best_K)

```


Therefore, we choose epsilon = 21 , minpoint = 3  as our parameter in this circumstances.


##Determine parameter

For K-means method, we take k = ?
